manuscript_outline

### 2025-06-21 docs/manuscript/paper.Rmd
edits

@@

As with any model of developmental timing, it is important to recognize that temperature is not the sole determinant of phenological events. For embryos, environmentally cued hatching is seen across taxa, wherein variation in hatch timing and developmental stage at hatching can result from myriad abiotic and biotic triggers [Warkentin 2011 <https://doi.org/10.1093/icb/icr017>]. While **hatchR** focuses specifically on temperature-dependent development, it can be integrated with complementary datasets or experimental manipulations to investigate these more complex, context-dependent interactions.

>>>>

**BCL Note: Not sure if it's a useful segue between these 2 case studies, but there's a cool paper on wood frog countergradient variation (Skelly 2004 <https://doi.org/10.1111/j.0014-3820.2004.tb01582.x>) that could be a useful eco-evo example of thinking species -\> population?**

@@

As with any model of developmental timing, it is important to recognize that temperature is not the sole determinant of phenological events. For embryos, environmentally cued hatching is seen across taxa, wherein variation in hatch timing and developmental stage at hatching can result from myriad abiotic and biotic triggers apart from temperature [Warkentin 2011 <https://doi.org/10.1093/icb/icr017>]. While **hatchR** focuses specifically on temperature-dependent development, it can be integrated with complementary datasets or experimental manipulations to investigate these more complex, context-dependent interactions.
